---
title: "Corona Virus Report"
author:
- familyname: XXXX
  othernames: XXX
  address: Monash Universtidy
  email: XXX
  correspondingauthor: true
  qualifications:  XXX
- familyname: XXXX
  othernames: Reports
  address: XXX
  qualifications: XXX
- familyname: XXX
  othernames: XXX
  address: XXX
  email: XXX
  correspondingauthor: true
  qualifications:  XXX
department: Our consultancy \newline add names &\newline add names
organization: Australian Government COVID19
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
---

```{r , echo = FALSE, message = FALSE, warning = FALSE}
# Libraries

library(tidyverse)
library(readr)
library(kableExtra)
library(bookdown)

```



\section*{Australia and USA}

```{r echo = FALSE, message = FALSE, warning = FALSE}
library(COVID19)
covidUSA <- covid19("USA")
covidGBR <- covid19("GBR")
```

We are interested in the impact of COVID19 on the United States of America (USA) and Great Britain (GBR).

From Table \@ref(tab:table) we can see that the countries have significantly different death rates with GBR having an average of 7.2% of confirmed cases resulting in death while USA is much lower at 2.8%.

```{r table}
covidUSAGBR <- bind_rows(covidUSA, covidGBR) %>%
  mutate(deathrate = 100*(deaths/confirmed)) %>%
  filter(!is.na(deathrate)) %>%
  select(id, date, deaths, confirmed, deathrate)

covidUSAGBR %>% summarise(mean(deathrate)) %>%
  kable()
```

We can also plot how this value changes over time. Figure \@ref(fig:plot) demonstrates this for both GBR and USA. As can be seen both countries start at a very low death rate for confirmed cases before increasing rapidly. This is followed by a period of steady decline. It should be noted however, that the USA has begun to see a second rise in the deathrate. This may be due to the easing of some restrictions or improvements in testing methods.

```{r plot}
covidUSAGBR %>%
  ggplot(aes(x = date, y = deathrate)) +
  geom_line() +
  facet_wrap(~ id) +
  ggtitle("Change in deathrate of COVID19 over time")
```


\section*{Country XX2 and YY2}

\section*{Country XX3 and YY3}



